Housing Manchester Handovers

### 2024-05-01 minos/validation/housing_manchester_handovers.Rmd
adding notebook for manchestere pop handovers

---
params:
    file_path: '' # default arguments. specify others in command line.
    intervention: ''
title: "Housing Default Handovers"
output:
  #output_file: "`r paste('minos/validation/', params$file_path, '_', params$intervention, '_handovers.html') `"
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide

@@

out.path <- here::here('output', 'energy_default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
#base.dat <- read_singular_local_out(out.path, 'goodHeatingDummy', drop.dead = TRUE)
```

>>>>

---
params:
    file_path: '' # default arguments. specify others in command line.
    intervention: ''
title: "Housing Manchester Handovers"
output:
  #output_file: "`r paste('minos/validation/', params$file_path, '_', params$intervention, '_handovers.html') `"
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide

@@

out.path <- here::here('output', 'energy_manchester_scaled/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
#base.dat <- read_singular_local_out(out.path, 'goodHeatingDummy', drop.dead = TRUE)
```
